Untitled

### 2024-11-05 code/manuscript_altanalysis.Rmd
more figures

df.z.temp %>% 
  #select(Zip, Year, DirectlyTreated, Att) %>% 
  mutate(Status = ifelse(Att == 0, NA, 
                         ifelse(Att > 0 & DirectlyTreated == 0, "IndirectlyTreated","DirectlyTreated"))) %>% 
  inner_join(census, by = c("Zip" = "ZipCode", "Year" = "YEAR")) %>% 
  filter(Year == 2012) %>% 
  mutate(PctMedicaid = Medicaid / MCD.denom * 100, 
         PctUninsured = Uninsured / Unins.denom * 100, 
         PctPoverty = IncomeBelowPoverty / PovertyStatusDet * 100, 
         PctBlack = Black / TotalPop * 100, 
         PctHispanic = Hispanic / TotalPop * 100) %>% 
    select(Status, TotalPop, PctMedicaid:PctHispanic) %>% 
    tbl_summary(by = Status, 
                statistic = list(all_continuous() ~ "{mean} ({sd})"), missing = "no") %>% 
  add_p()

@@

@@

>>>>

df.z.temp %>% 
  #select(Zip, Year, DirectlyTreated, Att) %>% 
  mutate(Status = ifelse(Att == 0, NA, 
                         ifelse(Att > 0 & DirectlyTreated == 0, "IndirectlyTreated","DirectlyTreated"))) %>% 
  inner_join(census, by = c("Zip" = "ZipCode", "Year" = "YEAR")) %>% 
  filter(Year == 2012) %>% 
  mutate(PctMedicaid = Medicaid / MCD.denom * 100, 
         PctUninsured = Uninsured / Unins.denom * 100, 
         PctPoverty = IncomeBelowPoverty / PovertyStatusDet * 100, 
         PctUnemployed = Unemployed / Unemp_denom * 100, 
         PctBlack = Black / TotalPop * 100, 
         PctHispanic = Hispanic / TotalPop * 100, 
         PctChildren = AgeUnder18 / TotalPop * 100, 
         PctElderly = Age65andOver / TotalPop * 100, 
         PctEducLow = EducLow / TotalPop * 100) %>% 
    select(Status, TotalPop, PctMedicaid:PctEducLow, UrbanRuralFlag) %>% 
    tbl_summary(by = Status, 
                statistic = list(all_continuous() ~ "{mean} ({sd})"), missing = "no") %>% 
  add_p()

@@

df.z.dist %>% 
  arrange(DistToClosestSite) %>% 
  ggplot(aes(x=DistToClosestSite)) + 
  geom_histogram(binwidth = 1, fill="lightgrey", color="white") + 
  xlim(0, 100) +
  stat_bin(aes(y=cumsum(..count..)/sum(..count..)*100 *3/2), binwidth = 1, geom="line", color="blue") + 
  scale_y_continuous(name = 'Number of Rivals', 
                     sec.axis = sec_axis(~.*2/3, name = "Cumulative percentage (%)")) + 
  theme_tufte_revised() + 
  ggtitle("FQHC Rivals by Distance from Service Area to New Competitive Zip") + 
  xlab("Distance Travelled (km)")

@@

# Save Datasets
```{r}
#df.z.temp %>% write_csv("/Users/markow/Dropbox/Git/Competition/data_processed/final_manuscript_allocation.csv")
#df.temptemp %>% write_csv("/Users/markow/Dropbox/Git/Competition/data_processed/final_manuscript_core.csv")
```
